Further Evidence of Modified Spin-down in Sun-like Stars:\\Pile-ups in the Temperature--Period Distribution

### 2022-03-29 src/ms.tex
changes to Gaia appendix

\section{The Gaia Color–Period Plane}\label{app:gaia}
\edit1{Given that the long-period pile-up was previously obscured by imprecise \teff measurements, we explored whether the feature could be recovered using the high precision photometric colors provided by the Gaia mission \citep{Gaia2016}. We cross-matched the \citet{McQuillan2014} sample with Gaia EDR3 \citep{GaiaEDR3}. We then compared the ($G_{BP}-G_{RP}$)–\prot distribution with constant Rossby curves. For this exercise, we used the empirically calibrated \taucz relation of \citet{Corsaro2021}, who presented \taucz as a quadratic function of Gaia $G_{BP}-G_{RP}$ color using the Kepler LEGACY asteroseismic sample as calibrators. We found that the long-period pile-up is clearly visible in the ($G_{BP}-G_{RP}$)–\prot plane once stars with high reddening ($A_V>0.2$) are excluded. In order to match a curve of constant Rossby number, given by $\mathrm{Ro}=\mathrm{Ro_\odot}=0.496$ on the \citet{Corsaro2021} scale, we found that a -0.1 mag shift to the Gaia colors of the data was required.}

@@

\software{\texttt{astropy} \citep{astropy13, astropy18}, 
          \texttt{corner} \citep{corner},
          \texttt{dustmaps} \citep{dustmaps}, 
          \texttt{emcee} \citep{emcee2013, emcee2019},
          \texttt{jupyter} \citep{jupyter},
          \texttt{matplotlib} \citep{matplotlib},
          \texttt{numpy} \citep{numpy},
          \texttt{pandas} \citep{pandas-soft, pandas-proc},
          \texttt{scipy} \citep{scipy},
          \texttt{seaborn} \citep{seaborn},
          \texttt{showyourwork!} \citep{Luger2021c}}

>>>>

\section{The Gaia Color–Period Plane}\label{app:gaia}
\edit1{Given that the long-period pile-up was previously obscured by imprecise \teff measurements, we explored whether the feature could be recovered using the high precision photometric colors provided by the Gaia mission \citep{Gaia2016}. We cross-matched the \citet{McQuillan2014} sample with Gaia EDR3 \citep{GaiaEDR3} using a 1 arcsec search radius and the \texttt{astroquery} package \citep{astroquery}. We computed reddening estimates for each target using the \texttt{dustmaps} package \citep{dustmaps}. We then compared the ($G_{BP}-G_{RP}$)–\prot distribution with constant Rossby curves. For this exercise, we used the empirically calibrated \taucz relation of \citet{Corsaro2021}, who presented \taucz as a quadratic function of Gaia $G_{BP}-G_{RP}$ color using the Kepler LEGACY asteroseismic sample as calibrators. We found that the long-period pile-up is clearly visible in the ($G_{BP}-G_{RP}$)–\prot plane once stars with high reddening ($A_V>0.2$) are excluded. In order to match a curve of constant Rossby number, given by $\mathrm{Ro}=\mathrm{Ro_\odot}=0.496$ on the \citet{Corsaro2021} scale, we found that a -0.1 mag shift to the Gaia colors of the data was required.}

@@

\software{\texttt{astropy} \citep{astropy13, astropy18},
          \texttt{astroquery} \citep{astroquery},
          \texttt{corner} \citep{corner},
          \texttt{dustmaps} \citep{dustmaps}, 
          \texttt{emcee} \citep{emcee2013, emcee2019},
          \texttt{jupyter} \citep{jupyter},
          \texttt{matplotlib} \citep{matplotlib},
          \texttt{numpy} \citep{numpy},
          \texttt{pandas} \citep{pandas-soft, pandas-proc},
          \texttt{scipy} \citep{scipy},
          \texttt{seaborn} \citep{seaborn},
          \texttt{showyourwork!} \citep{Luger2021c}}
